---
title: "P8105 HW6"
author: "Elaine Xu"
date: "12/5/2020"
output: github_document
---
```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(p8105.datasets)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

```{r, warning=FALSE, message=FALSE}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


## Problem 2

```{r, warning=FALSE, message=FALSE}
birthw = read_csv("./data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(
    babysex = factor(babysex),
    frace = factor(frace),
    mrace = factor(mrace),
    malform = factor(malform)
  )

sum(is.na(birthw))
```

#### fit a model for birth weight

I use Stepwise regression to find the variables that are most fit in the model.
```{r,eval=FALSE}
mult.fit <- lm(bwt ~ ., data=birthw)
step(mult.fit, direction='backward')
```

From the test result above, I got my model:
```{r}
model_fit1 = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + 
    mheight + mrace + parity + ppwt + smoken, data = birthw
)
summary(model_fit1)
```

After looking at the summary, I found out the p-value of `fincome` is greater than 0.05, and p-value of one of the `mrace` is also not significant. So I drop these two variables from my model. From the description, I think `bhead` and `blength` may overlap with `bwt`, so I dropped these two variables. After drop these three variables, `parity` becomes not significant, so I drop this variable too. Rebuild the model.

```{r}
model_fit1 = lm(bwt ~ babysex + delwt + gaweeks + 
    mheight + ppwt + smoken, data = birthw)
summary(model_fit1)
```

plot of residuals:
```{r}
birthw %>%
  add_residuals(model_fit1) %>%
  ggplot(aes(x = resid)) + geom_density()+
  labs(x = "Residuals")
```

plot of model residuals against fitted values:
```{r}
birthw %>%
  add_residuals(model_fit1) %>%
  add_predictions(model_fit1) %>%
  ggplot(aes(x = pred, y = resid)) + geom_point() +
  labs(x = "Fitted Value",
       y = "Residuals")
```
From the plot we cannot really see an obvious relation between the predictor and residuals.

#### Compare your model to two others

One using length at birth and gestational age as predictors (main effects only)
```{r}
model_fit2 = lm(bwt ~ blength + gaweeks, data = birthw)
```

One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
```{r}
model_fit3 = lm(bwt ~ blength + bhead + babysex + blength*bhead + blength* babysex + bhead*babysex + blength*bhead*babysex, data = birthw)
```

Cross validation:

```{r}
cv_df = 
  crossv_mc(birthw, 100) %>% 
    mutate(
        train = map(train, as.tibble),
        test = map(test,as.tibble)
    )  %>%
  mutate(
    model_fit  = map(train, ~lm(bwt ~ babysex + delwt + gaweeks + 
    mheight + ppwt + smoken, data = birthw)),
    model_fit2  = map(train, ~lm(bwt ~ blength + gaweeks, data = birthw)),
    model_fit3  = map(train, ~lm(bwt ~ blength + bhead + babysex + blength*bhead + blength* babysex + bhead*babysex + blength*bhead*babysex, data = birthw))) %>% 
  mutate(
    rmse_1 = map2_dbl(model_fit, test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(model_fit2 , test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(model_fit3, test, ~rmse(model = .x, data = .y))) 
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```
From the violin plot we can see that the model I made has the highest rmse value, which means the prediction accuracy for this model is too low to be used as a linear model. Model 3 has the lowest rmse, which is the model contains the interaction term. I would select model 3 with the interaction term to be my model.











